Place of death in NRS COVID-19 deaths

### 2021-01-27 covid_nrs_place_of_death.Rmd
fixed problem with place of death ordering in plot 6

annotations_figure_6 <-
# datapasta::tribble_paste(tbl_recoded_place_of_death %>% select(place_of_death_recoded))
  tibble::tribble(
    ~place_of_death_recoded, ~x, ~y, ~label,
                 "Hospital", 35L, 800, "Hospital deaths dipped below historical minimum and remained low until Winter.",
                 "Hospital", 35L, 250, "Shaded area shows range of deaths 2015-2019 dashed line shows weekly average",
                "Care home", 35L, 500, "After initial peak, deaths returned to historical range; non-Covid deaths remained low.",
                     "Home", 35L, 500, "The gap between historical\nhigh and both types of death\nat home was high throughout."
                  )

merged_data %>% 
  filter(sex == "all" & age == "all") %>%
  filter(!place_of_death_recoded %in% c("All","Other")) %>%
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid_related), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = week_number_run_over)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  # geom_line(aes(y = deaths_all_causes)) +
  # geom_line(aes(y = deaths_non_covid_related), colour = "red") +
  geom_line(aes(y = deaths_mean), linetype = "dashed", size = 0.2) +
  geom_vline(xintercept = 54, linetype = "dotted") +
  geom_text(data = annotations_figure_6, aes(x=x,y=y, label=label)) +
  scale_x_continuous(breaks = seq(0,60,by=10)) +
  facet_grid(~place_of_death_recoded) +
  theme_minimal() +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(legend.position = "top", plot.caption = element_text(size = 10, colour = "gray60")) +
  labs(x = "Week number",
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(vertical_line_text, removed_other_category_text, source_nrs_text), collapse="\n")
       )
```

>>>>

annotations_figure_6 <-
# datapasta::tribble_paste(tbl_recoded_place_of_death %>% select(place_of_death_recoded))
  tibble::tribble(
    ~place_of_death_recoded, ~x, ~y, ~label,
                 "Hospital", 35L, 800, "Hospital deaths dipped below historical minimum and remained low until Winter.",
                 "Hospital", 35L, 250, "Shaded area shows range of deaths 2015-2019 dashed line shows weekly average",
                "Care home", 35L, 500, "After initial peak, deaths returned to historical range; non-Covid deaths remained low.",
                     "Home", 35L, 500, "The gap between historical\nhigh and both types of death\nat home was high throughout."
                  ) %>% 
  mutate(place_of_death_recoded = factor(place_of_death_recoded, levels = levels(tbl_recoded_place_of_death$place_of_death_recoded)))  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!

merged_data %>%
  filter(sex == "all" & age == "all") %>%
  filter(!place_of_death_recoded %in% c("All","Other")) %>%
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid_related), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = week_number_run_over)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", size = 0.2) +
  geom_vline(xintercept = 54, linetype = "dotted") +
  geom_text(data = annotations_figure_6, aes(x=x,y=y, label=label)) +
  scale_x_continuous(breaks = seq(0,60,by=10)) +
  facet_grid(~place_of_death_recoded) +
  theme_minimal() +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(legend.position = "top", plot.caption = element_text(size = 10, colour = "gray60")) +
  labs(x = "Week number",
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(vertical_line_text, removed_other_category_text, source_nrs_text), collapse="\n")
       )
```
